Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-06 cmsb22.tex
Removed useless stuff

\begin{abstract}
  % The abstract should briefly summarize the contents of the paper in
  % 150--250 words.

@@

\sylvain{I might add a small figure for the example later\dots}
\vangiang{In this small figure, we can show the STG under the fully asynchronous update and the Petri net encoding of the Boolean model.}

@@

\sylvain{It seems that the RA\_apoptosis model is only 180 nodes, where does the n = 431 come from?}
\vangiang{n = 431 comes from Table 1 of~\cite{aghamiri2020automated}. I have checked this model. It has only 180 nodes. I will check others models come from~\cite{aghamiri2020automated}.}

@@

\sylvain{the \texttt{dom-pref} thing is deprecated since 2014 but still used in PyBoolNet, I think we might give the more modern version I used in the Python script, but we'll see}
\vangiang{I also found that you did not use the \texttt{dom-pref} thing in the Python script. I think we should use the same configuration as that used in PyBoolNet.}

% \subsection{Benchmark vs.\ implicant-based methods}

>>>>

\begin{abstract}

@@

\vangiang{In this small figure, we can show the STG under the fully asynchronous update and the Petri net encoding of the Boolean model.}

@@

\vangiang{n = 431 comes from Table 1 of~\cite{aghamiri2020automated}. I have checked this model. It has only 180 nodes. I will check others models come from~\cite{aghamiri2020automated}.}
\sylvain{that's actually another model (called RA-map or something in the supplementary material), I think the other models should be ok.}

@@

\sylvain{the \texttt{dom-pref} thing is deprecated since 2014 but still used in PyBoolNet, I think we might give the more modern version I used in the Python script, but we'll see}
\vangiang{I also found that you did not use the \texttt{dom-pref} thing in the Python script. I think we should use the same configuration as that used in PyBoolNet.}
\sylvain{as said above, this is deprecated, and has been since August 2014 \url{https://github.com/potassco/clasp/blob/master/CHANGES}, so I'd advise against using it, it might break any-time.}
